---
title: "Primary Outcomes Completion Report"
date: today
format:
  html:
    toc: true
    html-math-method: katex
    embed-resources: true

execute:
  echo: false
  warning: false
---

```{r, echo = FALSE, eval = FALSE}
################################################################################
# Carlos Rodriguez, PhD. CU Anschutz, Dept. of Fam. Medicine
# Helpers stay quit - primary completion report

# This report is designed to count frequencies and proportions of the missing
# and non-missing values for the primary and secondary outcomes as defined in
# the statistical analysis plan for the HSQ project.

# In addition, this report scores and summarizes the instruments used in the 
# HSQ surveys. This report does not manipulate any of the network measures.
# Those are handled by a different script.
################################################################################
```

```{r, load libraries, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

pacman::p_load(here,
               tidyverse,
               magrittr,
               gtsummary,
               Hmisc, 
               gt,
               install = FALSE)
```

```{r}
source("C:\\Users\\rodrica2\\OneDrive - The University of Colorado Denver\\Documents\\DFM\\projects\\hsq\\scripts\\compile_data\\prep_long_data.R")
```

```{r}
#| eval: false

# This section is designed to output a .csv file showing the response rates to 
# the longitudinal surveys using se5 for baseline, and fu_smoke1 for the 
# following timepoints (3m, 6m, 9m, and 12m). Requested by Jun Ying for data 
# qa purposes.

longitudinal_response_rates <- 
# 0mo
left_join(
  data_lst[[1]] %>% 
    select(record_id, arm, se5) %>% 
    mutate(
      due_for_0m = 1, 
      complete_0m = ifelse(!is.na(se5), 1, 0)) %>% 
    select(-se5),

  # 3mo
  data_lst[[2]] %>% 
    select(record_id, fu_smoke1) %>% 
    mutate(
      due_for_3m = 1, 
      complete_3m = ifelse(!is.na(fu_smoke1), 1, 0)) %>% 
    select(-fu_smoke1),
  by = "record_id") %>%

left_join(
  # 6mo
  data_lst[[3]] %>% 
    select(record_id, fu_smoke1) %>% 
    mutate(
      due_for_6m = 1, 
      complete_6m = ifelse(!is.na(fu_smoke1), 1, 0)) %>% 
    select(-fu_smoke1),
  by = "record_id") %>%

left_join(
  # 9mo
  data_lst[[4]] %>% 
    select(record_id, fu_smoke1) %>% 
    mutate(
      due_for_9m = 1, 
      complete_9m = ifelse(!is.na(fu_smoke1), 1, 0)) %>% 
    select(-fu_smoke1),
  by = "record_id") %>%

left_join(
  # 12mo
  data_lst[[5]] %>% 
    select(record_id, fu_smoke1) %>% 
    mutate(
      due_for_12m = 1, 
      complete_12m = ifelse(!is.na(fu_smoke1), 1, 0)) %>% 
    select(-fu_smoke1),
  by = "record_id")

longitudinal_response_rates %<>%
  mutate(across(due_for_6m:complete_12m, ~ ifelse(is.na(.x), 0, .x)))

longitudinal_response_rates %<>%
  left_join(
    data %>% 
      select(record_id, hsqid) %>% 
      distinct() %>% 
      filter(record_id %in% longitudinal_response_rates$record_id),
    by = "record_id") %>% 
  select(-record_id) %>% 
  select(hsqid, arm, everything())

write_csv(longitudinal_response_rates, file = "C:\\Users\\rodrica2\\OneDrive - The University of Colorado Denver\\Documents\\DFM\\projects\\hsq\\scripts\\primary_outcomes_completion_report\\response_rates\\longitudinal_response_rates.csv")
```

```{r, data_lst indexes}
# data_lst indexes
# 1 ~ 0mo
# 2 ~ 3mo
# 3 ~ 6mo
# 4 ~ 9mo
# 5 ~ 12mo
```

```{r}

```

# Total number of randomized patients in RedCap to date
```{r}
# Use the baseline survey time point to display the total number of randomized patients
data_lst[[1]] %>%
  select(arm) %>%
  rename(Arm = arm) %>%
  tbl_summary(digits = everything() ~ c(0,1))
```

# Demographics 
```{r}
data_lst[[1]] %>% 
  select(Arm, Age, Gender, Hispanic:Declined) %>%
  tbl_summary(by = Arm,
    statistic = list(Age ~ "{mean} ({sd})")) %>%
  add_variable_group_header(
    header = "Race", 
    variables = c(
      "Black or African American",
      "Asian",
      "White/Caucasian",
      "Native Hawaiian or other Pacific Islander",
      "American Indian/Alaska Native",
      "Other",
      "Declined"), 
    indent = 4L)
```

# Primary Outcomes

## Primary Outcomes: Smoking status (30-day and 7-day point prevalence abstinence) at 6- and 12- months
```{r}
# Filter individuals who are eligible at each time point
# Eligibility defined as being in the study 180 + 14 days past randomization
```

#### Have you smoked cigarettes in the past 30 days (even a puff)?
- Denominator includes those that have been enrolled in the study for the 6 or 12 months plus a 14-day grace period to complete the survey.
```{r}
data_lst[c(3,5)] %>%
  purrr::map(
    ~.x %>%
    select(fu_smoke1) %>%
    mutate(
      fu_smoke1 = ifelse(is.na(fu_smoke1), "Missing", "Not Missing")) %>%
    tbl_summary(
      type = all_dichotomous() ~ "categorical",
      label = fu_smoke1 ~ "Smoked in past 30 days")
  ) %>%
    tbl_merge(., tab_spanner = c("**6mo**", "**12mo**"))
```

```{r}
#| eval: false
# Placed here to deliver a table to Jun for the missing rates of one 
# question from the longitudinal data
long_data_missing <- data_lst[c(2, 3, 4, 5)] %>%
  purrr::map( ~.x %>%
                select(fu_smoke1, arm) %>%
                mutate(fu_smoke1 = ifelse(is.na(fu_smoke1), "Missing", "Not Missing")) %>%
                tbl_summary(by = arm, type = all_dichotomous() ~ "categorical",
                            label = fu_smoke1 ~ "Smoked in past 30 days") %>%
                add_p()       
              ) %>%
  tbl_merge(.,
          tab_spanner = c("**3mo**", "**6mo**", "**9mo**", "**12mo**"))

long_data_missing %>%
  as_gt() %>%
  gt::gtsave(filename = "C:\\Users\\rodrica2\\OneDrive - The University of Colorado Denver\\Documents\\DFM\\projects\\hsq\\scripts\\missing_rates_by_arm.docx") # use extensions .png, .html, .docx, .rtf, .tex, .ltx

```

#### Have you smoked cigarettes in the past 7 days (even a puff)?
- Denominators includes those that have been enrolled in the study for the 6 or 12 months plus a 14-day grace period to complete the survey.
- "No" responses from 30-day time point carried over to 7-day time point
```{r}
data_lst[c(3,5)] %>%
  purrr::map(
    ~.x %>%
    mutate(fu_smoke5 = ifelse(fu_smoke1 == "No", "No", fu_smoke5)) %>%
    select(fu_smoke5) %>%
    mutate(fu_smoke5 = ifelse(is.na(fu_smoke5), "Missing", "Not Missing")) %>%
    tbl_summary(type = all_dichotomous() ~ "categorical",
                label = fu_smoke5 ~ "Smoked in past 7 days")
  ) %>%
  tbl_merge(., tab_spanner = c("**6mo**", "**12mo**"))
```

# Secondary Outcomes: 

## The timing of participants’ first relapse to smoking (secondary outcome)
Timing of first relapse is derived from SMS surveys which are administered weekly for weeks 1 through 24 and bi-weekly thereafter.
```{r}
# pull SMS data
# remove week 0, since it's more of a record keeping row
# Group by week total number of rows is the denominator, for each week,
# then count the number of those that responded vs not responded.
```

```{r, echo = FALSE}
# Define get_redcap_report function which will retrieve a report from a given
# RedCap project according to the report_id (assigned in RedCap)
get_redcap_report <- function (token, report_id, labels = "raw"){
    url <- "https://redcap.ucdenver.edu/api/"

   formData <- list(token = token, content = "report", format = "csv",
        report_id = report_id, csvDelimiter = "", rawOrLabel = labels,
        rawOrLabelHeaders = "raw", exportCheckboxLabel = "false",
        returnFormat = "csv")

    response <- httr::POST(url, body = formData, encode = "form")

    result <- httr::content(response)

    return(result)
}
```

```{r, echo = FALSE}
# Retrieve SMS data from HSQ SMS Survey report
sms <- get_redcap_report(token = Sys.getenv("HSQ_sms"),
                                   report_id = "117325")
```

```{r, echo = FALSE, eval=FALSE}
# If warning arises, use problems() to investigate.
# warning arises because sms_survey_timestamp contains "[not completed]"
problems(sms)
```

```{r, echo = FALSE}
# Process the sms data set, by creating rows for which patients did not submit
# an sms survey, in order to calculate the actual number of missing data
sms %<>%
  complete(record_id, redcap_event_name) %>% # Introduce rows with missing values for each possible sms week
  group_by(record_id) %>%
  fill(randomization_dtd, .direction = "downup") %>%
  fill(sms_strt_dtd, .direction = "downup") %>%
  fill(hsqid, .direction = "downup") %>%
  fill(patientend_dtd, .direction = "downup") %>%
  ungroup() %>%
  filter(redcap_event_name != "week0_arm_1") %>% # this row contains housekeeping data and is not of interest
  mutate(redcap_event_name = str_replace_all(redcap_event_name,
                                             c("week1_" = "week01_",
                                               "week2_" = "week02_",
                                               "week3_" = "week03_",
                                               "week4_" = "week04_",
                                               "week5_" = "week05_",
                                               "week6_" = "week06_",
                                               "week7_" = "week07_",
                                               "week8_" = "week08_",
                                               "week9_" = "week09_"))) %>%
  mutate(redcap_event_name = str_replace(redcap_event_name, "_arm_1", "")) %>%
  mutate(weeks_since_rand = round(difftime(Sys.Date(), as.Date(randomization_dtd), unit = "weeks"))) %>%
  mutate(week = as.numeric(str_replace(redcap_event_name, "week", ""))) %>%
  arrange(record_id, week) %>%
  select(-redcap_survey_identifier) %>%
  mutate(sms_strt_dtd = as.Date(sms_strt_dtd),
         sms_survey_timestamp = as.Date(sms_survey_timestamp))

# Determine the length of time in weeks each participant has been enrolled in 
# the study, starting from the randomization date
weeks_in_study <-
  sms %>%
  select(record_id, weeks_since_rand) %>%
  group_by(record_id) %>%
  slice_head() %>%
  ungroup()
```

```{r, echo = FALSE}
# Create a wide dataframe from sms based off of the smoke1 variable
wide <- sms %>%
  # mutate(smoke1 = ifelse(is.na(smoke1), "Missing", "Not Missing")) %>%
  select(record_id, redcap_event_name, smoke1) %>%
  group_by(record_id) %>%
  pivot_wider(names_from = redcap_event_name, values_from = smoke1) %>%
  ungroup()

# Get the names of the columns, except for record_id in the wide data frame
col_names <- names(wide %>% select(-record_id))

# Sort the names of the columns as they will determine how to place the Week #
# in order for displaying in a table
col_names <- col_names %>% sort()

# Reorder the columns in the order of weeks
wide %<>%
  select(record_id, all_of(col_names))

# Join wide with weeks in the study for each participant
wide <- left_join(wide, weeks_in_study, by = "record_id")
```

```{r}
#| eval: false

# This section is designed to output a .csv file showing the response rates to the question
# fu_smoke1 from the sms surveys.

# uses the wide data frame
for (i in 2:37){
  col_name <- names(wide[,i])
  due_name <- str_c("due_for_", col_name)
  week_num <- as.numeric(substring(col_name, nchar(col_name) -1))

  wide %<>%
    mutate(!!sym(due_name) := ifelse(week_num <= as.numeric(weeks_since_rand), 1, 0))

}

sms_response_rates <- wide %>%
  mutate(across(week01:week48, ~ ifelse(is.na(.x), 0, 1)))

# rename and reorder the columns
sms_names <- names(sms_response_rates)
sms_names[2:37] <- str_c("complete_", sms_names[2:37])

names(sms_response_rates) <-  sms_names

week_indexes <- 2:37

due_index <- 39:74

ordered_names <- c()

for (i in 1:36) {
  ordered_names <- c(ordered_names, sms_names[week_indexes[i]])

  ordered_names <- c(ordered_names, sms_names[due_index[i]])
}


sms_response_rates %<>%
  select(record_id, weeks_since_rand, all_of(ordered_names))

# Merge in an HSQ id
sms_response_rates %<>% 
  left_join(
    sms %>%
      select(record_id, hsqid) %>%
      distinct(),
    by = "record_id")

sms_response_rates %<>% select(-record_id)

sms_response_rates %<>% select(hsqid, everything())

write_csv(sms_response_rates, file = "C:\\Users\\rodrica2\\OneDrive - The University of Colorado Denver\\Documents\\DFM\\projects\\hsq\\scripts\\primary_outcomes_completion_report\\response_rates\\sms_response_rates.csv")
```

```{r, echo = FALSE}
# For each column, determine which ids should be included at a given time point
# If a patient has only been enrolled for two weeks, they should not be included
# in counts for the number of missing values of the 4 week time point bc they
# haven't been in the study long enough.
create_weeks_table <- function(data){
  # Create an empty data frame to eventually convert into a gt table
  output_tbl <-  NULL

  # For each week, only the number of participants that are eligible, will be
  # counted for the number of missing/not missing values
    for (i in 1:length(col_names)){
  
    # set the week to filter the data
    week <- as.numeric(str_replace(col_names[i], "week", ""))
  
    tbl <- data %>%
      filter(weeks_since_rand >= week) %>%
      select(all_of(col_names[i])) %>%
      mutate(across(everything(), ~ ifelse(is.na(.), "Missing", "Not Missing"))) %>%
      tbl_summary() %>%
      as_tibble()
    
    # Capture the table names to be able to index dynamically when converting to 
    # wide
    tbl_names <- names(tbl)
    
    # convert tbl to wide using the index column names
    tbl %<>% 
      pivot_wider(names_from = tbl_names[1], 
                  values_from = tbl_names[2])
    
    # Create a new column indicating the week
    tbl %<>% mutate(Week = week)
    
    # Select columns and then re-order
    tbl %<>% 
      select(Missing:Week) %>%
      select(Week, everything())
    
    # Capture the number of rows available for calculating frequencies and 
    # proportions for each week
    N_rows <- 
      wide %>% 
      filter(weeks_since_rand >= week) %>% 
      nrow()
    
    # Create a new column with the total number of participants with available
    # data for each week
    tbl %<>% 
      mutate(N = N_rows) %>%
      select(Week, N, Missing, everything())
    
    # Append each new week's data to the next
    output_tbl <- bind_rows(output_tbl, tbl)
  
    }
   return(output_tbl)
}

output_tbl <- create_weeks_table(wide)
```

```{r, echo = FALSE, eval=FALSE}
output_tbl %>% gt()
```

```{r, echo = FALSE}
################## PREPARE TIME TO EVENT DATA ##################################
# Get the average or min/max of days between the date the sms survey is 
# scheduled to be delivered and the survey time stamp. The rationale for 
# discovering this is to determine how to assign a survey time stamp for 
# patients who responded to smoke1, but did not submit their survey causing
# RedCap to not record a survey timestamp.

# avg_t_to_submit DOES NOT NEED TO BE RUN EVERY SINGLE TIME
# avg_t_to_submit <- 
# sms %>%
#   drop_na(sms_survey_timestamp) %>%
#   mutate(first_half = ifelse(week < 24, 1, 0)) %>%
#   # filter(record_id == 105) %>%
#   select(record_id, week, randomization_dtd, sms_strt_dtd, sms_survey_timestamp, first_half) %>%
#   
#   # sms_strt_dtd reflects the date that the sms messages started. Calculate the 
#   # date the sms message is sent for each week.
#   mutate(sms_sent_dtd = sms_strt_dtd + ((week-1) * 7)) %>%
#   
#   # count the number of days between the time stamp and the sent date
#   # some sms messages will get sent out early and result in a negative time
#   mutate(since_sms_sent_dtd = sms_survey_timestamp - sms_sent_dtd) %>%
#   
#   # remove rows with negative values, because some participants had issues in
#   # RedCap where they did not receive week 1 record_ids 227-236
#   filter(since_sms_sent_dtd >= 0) %>%
#   select(record_id, since_sms_sent_dtd, first_half) %>%
#   group_by(record_id, first_half) %>%
#   summarise(across(since_sms_sent_dtd, ~ round(mean(.x)))) %>%
#   ungroup() %>%
#   group_by(first_half) %>%
#   select(since_sms_sent_dtd) %>%
#   summarise_all(list(mean = mean, min = min, max = max)) %>%
#   ungroup() %>%
#   mutate(across(everything(), ~ round(.x)))
```

```{r}
# Based on code chunk above, on average, it takes 0 days for participants to submit their sms surveys
t_submit <- 0
```

```{r}
# Create an intermediary data frame where only patients that relapsed are 
# retained, sort by date, then select the first available row to capture the 
# date of the first relapse. Time stamps are then converted to dttm format as an
# intermediary step to convert to as.Date(). The randomization dates are then 
# subtracted from the time stamp to calculate the time to the first relapse.
first_relapse <- 
  sms %>%
  filter(smoke1 == 1) %>% 
  mutate(sms_survey_timestamp = if_else(is.na(sms_survey_timestamp) & !is.na(smoke1), 
                                        (sms_strt_dtd + ((week-1) * 7 + t_submit)), sms_survey_timestamp)) %>%
  arrange(record_id, sms_strt_dtd) %>%
  group_by(record_id) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(sms_survey_timestamp = as.POSIXct(sms_survey_timestamp)) %>%
  mutate(across(c(sms_strt_dtd, sms_survey_timestamp), ~ as.Date(.))) %>%
  mutate(time_to_relapse = sms_survey_timestamp - randomization_dtd) %>%
  select(record_id, time_to_relapse)
```

```{r}
# Includes partially completed surveys, by estimating a sms_survey_timestamp as
# the sum of the sms start date and the week-1 number * 7 days plus 2 to 
# estimate the date of the last observation, otherwise the last observation is 
# the last fully complete response.
last_observation <-
  sms %>% 
  mutate(sms_survey_timestamp = if_else(is.na(sms_survey_timestamp) & !is.na(smoke1), 
                                        (sms_strt_dtd + ((week-1) * 7 + t_submit)), sms_survey_timestamp)) %>%
  arrange(record_id, week) %>%
  drop_na(smoke1) %>%
  group_by(record_id) %>%
  slice_tail() %>%
  ungroup() %>%
  mutate(last_obs_dtd = as.POSIXct(sms_survey_timestamp)) %>%
  mutate(across(c(sms_strt_dtd, sms_survey_timestamp), ~ as.Date(.))) %>%
  mutate(time_to_last_obs = sms_survey_timestamp - randomization_dtd) %>%
  select(record_id, time_to_last_obs)
```

```{r}
# Create a data set that displays the number of days to the first relapse
# One row per patient. In this data frame, those with missing time represent
# true missing values. 
t_to_relapse <- 
  sms %>%
  select(record_id, hsqid, randomization_dtd, sms_strt_dtd) %>%
  group_by(record_id) %>%
  slice_head() %>%
  ungroup() %>%
  left_join(., first_relapse, by = "record_id") %>%
  left_join(., last_observation, by = "record_id") %>%
  mutate(event = ifelse(is.na(time_to_relapse), 0, 1),
         time = ifelse(is.na(time_to_relapse), time_to_last_obs, time_to_relapse),
         status = ifelse(event == 1, "relapse", "abstain")) %>%
  mutate(across(c(event, status), ~ifelse(is.na(time), NA, .)))

# Add in State/quitline info, HSQID, age, sex, gender, race.ethnicity, and treatment
t_to_relapse <- 
left_join(t_to_relapse,
          (data_lst[[1]] %>%  select(hsqid, arm, age, gender, eth, race___0:race____1, quitline)),
          by = "hsqid")
```

```{r}
# Before outputing to SAS. Convert dates to strings and save with na = ''
# Output t_to_relapse to .csv file for SAS
t_to_relapse %>%
  mutate_if(is.Date, as.character) %>%
  mutate_if(is.difftime, as.numeric) %>%
  write_csv(here("analyses_sas", "data", "first_relapse.csv"), na = "")
```

"Missing" identifies individuals who did not answer any of sms survey smoke1 questions. "Not Missing" identifies individuals who answered at least one sms survey and includes individuals who partially completed sms surveys. Both time and event variables are required for time to event analysis
```{r}
# Table of the missing and non-missing values
t_to_relapse %>%
  select(time, event) %>%
  mutate(across(everything(), ~ ifelse(is.na(.), "Missing", "Not Missing"))) %>%
  tbl_summary()
```

```{r, eval = FALSE}
# Check to see how long it usually takes to receive the sms_strt_dtd after the
# randomization date.
# sms survey typically starts 4 days after randomization, but could be as early
# as within randomization and 14 days after randomization.
sms %>% 
  group_by(record_id) %>% 
  slice_head() %>% 
  ungroup() %>% 
  mutate(sms_strt_dtd = as.Date(as.POSIXct(sms_strt_dtd))) %>% 
  mutate(time_btw = sms_strt_dtd - randomization_dtd) %>% 
  select(time_btw) %>%
  summarise(mean = mean(time_btw), 
            stdev = sd(time_btw),
            min = min(time_btw),
            max = max(time_btw))
```

```{r, echo = FALSE, eval = FALSE}
# Display the proportion of abstainers and relapsers at each week of the sms
# surveys
# create_weeks_table <- function(data){
#   # Create an empty data frame to eventually convert into a gt table
#   output_tbl <-  NULL
# 
#   # For each week, only the number of participants that are eligible, will be
#   # counted for the number of missing/not missing values
#     for (i in 1:length(col_names)){
#   
#     # set the week to filter the data
#     week <- as.numeric(str_replace(col_names[i], "week", ""))
#   
#     tbl <- data %>%
#       filter(weeks_since_sms_strt >= week) %>%
#       select(all_of(col_names[i])) %>%
#       mutate(across(everything(), ~ case_match(., 
#                                          0 ~ "Abstain",
#                                          1 ~ "Relapse"))) %>%
#       mutate(across(everything(), ~ factor(.))) %>%
#       mutate(across(everything(), ~ fct_na_value_to_level(., level = "Missing"))) %>%
#       tbl_summary() %>%
#       as_tibble()
#     
#     # Capture the table names to be able to index dynamically when converting to 
#     # wide
#     tbl_names <- names(tbl)
#     
#     # convert tbl to wide using the index column names
#     tbl %<>% 
#       pivot_wider(names_from = tbl_names[1], 
#                   values_from = tbl_names[2])
#     
#     # Create a new column indicating the week
#     tbl %<>% mutate(Week = week)
#     
#     # Select columns and then re-order
#     tbl %<>% 
#       select(Abstain:Week) %>%
#       select(Week, everything())
#     
#     # Capture the number of rows available for calculating frequencies and 
#     # proportions for each week
#     N_rows <- 
#       wide %>% 
#       filter(weeks_since_sms_strt >= week) %>% 
#       nrow()
#     
#     # Create a new column with the total number of participants with available
#     # data for each week
#     tbl %<>% 
#       mutate(N = N_rows) %>%
#       select(Week, N, Missing, everything())
#     
#     # Append each new week's data to the next
#     output_tbl <- bind_rows(output_tbl, tbl)
#   
#     }
#    return(output_tbl)
# }
# 
# output_tbl <- create_weeks_table(wide)
# 
# output_tbl %>% gt::gt()

```

## Rates of participants’ self-reported delivery of HCs to other tobacco users (secondary outcome).
```{r}
wide_help1 <- sms %>%
  select(record_id, redcap_event_name, help1) %>%
  group_by(record_id) %>%
  pivot_wider(names_from = redcap_event_name, values_from = help1) %>%
  ungroup()

col_names <- names(wide_help1 %>% select(-record_id))

col_names <- col_names %>% sort()

# Reorder the columns in the order of weeks
wide_help1 %<>%
  select(record_id, all_of(col_names))

# Join the wide_help1
wide_help1 <- left_join(wide_help1, weeks_in_study, by = "record_id")
```

```{r, echo = FALSE}
output_tbl <- create_weeks_table(wide_help1)
```

```{r, echo = FALSE}
output_tbl %>% gt::gt()
```

## Smoking status (30-day and 7-day point prevalence abstinence) at 3- and 9- months
```{r}
# Filter individuals who are eligible at each time point
# Eligibility defined as being in the study 180 + 14 days past randomization
```

#### Have you smoked cigarettes in the past 30 days (even a puff)?
- Denominator includes those that have been enrolled in the study for the 6 or 12 months plus a 14-day grace period to complete the survey.
```{r}
data_lst[c(2,4)] %>%
  purrr::map(
    ~.x %>%
    select(fu_smoke1) %>%
    mutate(fu_smoke1 = ifelse(is.na(fu_smoke1), "Missing", "Not Missing")) %>%
    tbl_summary(type = all_dichotomous() ~ "categorical")
  ) %>%
  tbl_merge(., tab_spanner = c("**3mo**", "**9mo**"))
```

#### Have you smoked cigarettes in the past 7 days (even a puff)?
- Denominator includes those that have been enrolled in the study 104 days (3 months = 90 days, plus a 14-day period to complete the survey)
- "No" responses from 30-day time point carried over to 7-day time point
```{r}
data_lst[c(2,4)] %>%
  purrr::map(
    ~.x %>%
    mutate(fu_smoke5 = ifelse(fu_smoke1 == "No", "No", fu_smoke5)) %>%
    select(fu_smoke5) %>%
    mutate(fu_smoke5 = ifelse(is.na(fu_smoke5), "Missing", "Not Missing")) %>%
    tbl_summary(type = all_dichotomous() ~ "categorical")
  ) %>%
  tbl_merge(., tab_spanner = c("**3mo**", "**9mo**"))
```

```{r}
# Declare the spanner vector for labelling tables where all timepoints are 
# displayed.
spanner <- c("**0mo**", "**3mo**", "**6mo**", "**9mo**", "**12mo**")
```

## PHQ4
### Missing values of total summed scores of the PHQ4 (psychological distress), Anxiety (items 1-2), and Depression (items 3-4)
```{r}
# Display the data              
data_lst %>%
  purrr::map(
    ~.x %>%                
    select(PHQ4, Anxiety, Depression) %>%
    tbl_summary()
  ) %>%
  tbl_merge(.,tab_spanner = spanner)
```

### Anxiety, depression, and psychological distress scores
Displays the overall anxiety, depression, and psychological distress scores of the PHQ4. Psychological distress combines the anxiety and depression subscales by computing a sum across all 4 questions, and categorizing into levels of severity based on predefined cut points. Responses with missing values were included in summed scores (i.e. includes participants who did not complete all 4 questions).
- Total sum score of psychological distress:
- 0-2 - None     
- 3-5 - Mild
- 6-8 - Moderate
- 9-12 - Severe
```{r}
# Create a table of the separate anxiety and depression scores along with the
# overall psychological distress scores and their categorical frequencies and 
# proportions
data_lst %>%
  purrr::map(
    ~.x %>%
    select(anx_score, dep_score, psy_score, psy_cat) %>%
    tbl_summary(
      type = list(
        anx_score ~ "continuous",
        dep_score ~ "continuous"),
      statistic = list(all_continuous() ~"{mean} ({sd})"))
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```

## Abstinence-related motivational engagement (ARME) scale
### Missing values of total summed scores
Missing is defined as a response where all questions from the ARME were missing and thus a summed scored was not able to be computed.
```{r}
# Create a list of the tbl_summary() outputs from the ARME variable
data_lst %>%
  purrr::map(
    ~.x %>%
    select(ARME) %>%
    tbl_summary()         
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```

### Summary of summed ARME scores
```{r}
data_lst %>%
  purrr::map( 
    ~.x %>%
    select(arme_score) %>%
    tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})"))
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```

## Confidence Self-Efficacy
### Missing values of percentage scores
```{r}
# Create a list of the tbl_summary() outputs from the SE variable
data_lst %>%
  purrr::map(
    ~.x %>%
    select(SE_c) %>%
    tbl_summary()
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```

### Summary of percent confidence scores
Percentage scores lie on a range from 0 to 100 where 100 indicates Very confident across all items and a 0 indicates Not at all confident across all items.
```{r}
data_lst %>%
  purrr::map(
    ~.x %>%
    select(se_conf_score) %>%
    tbl_summary(statistic = list(everything() ~ "{mean} ({sd})"))
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```


## Skills Self-Efficacy
### Missing values of mean scores
```{r}
data_lst %>%
  purrr::map(
    ~.x %>%
    select(SE_s) %>%
    tbl_summary()
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```

### Summary of mean skills scores
Skill scores lie on a range between -3 and +3 where +3 indicates Very sure I am able to... and -3 indicates Not at all sure I am able to....
* "Not at all sure I am able to" ~ -3,
* "Usually not sure I am able to" ~ -2,
* "Somewhat not sure I am able to" ~ -1,
* "Neutral" ~ 0,
* "Somewhat sure I am able to" ~ 1,
* "Usually sure I am able to" ~ 2,
* "Very sure I am able to" ~ 3,
```{r}
data_lst %>%
  purrr::map(
    ~.x %>%
    select(se_skill_score) %>%
    tbl_summary(statistic = list(everything() ~ "{mean} ({sd})"))
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```

## Proactive coping scale
### Missing values of total summed scores
```{r}
# Create a list of the tbl_summary() outputs from the PCS variable
data_lst %>%
  purrr::map(
    ~.x %>%
    select(PCS) %>%
    mutate(PCS = factor(PCS, levels = c("Missing", "Not Missing"))) %>%
    tbl_summary()         
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```

### Summed scores
Summed scores lie on a range of 14 to 56 where higher values indicate higher future oriented coping (effectively managing stressful events).
```{r}
# Display the mean and sd of the pcs_score
data_lst %>%
  purrr::map(
    ~.x %>%
    select(pcs_score) %>%
    tbl_summary(statistic = all_continuous() ~ "{mean} ({sd})")
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```

## COGDIS
Measures residual attraction (att) to smoking, smoker identity (idn), and vulernability to smoking relapse (vul).

### Missing values of COGDIS scores
```{r}
# Create a list of the tbl_summary() outputs from the CD variable
data_lst %>%
  purrr::map( 
    ~.x %>%
    select(CD_att:CD_vul) %>%
    tbl_summary()
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```

### Summary of COGDIS scores
COGDIS scores are dichotomous indicators, positive screens for residual attraction, smoking identity, and vulernability to smoking relapse.
```{r}
data_lst %>%
  purrr::map( 
    ~.x %>%
    select(cd_attraction:cd_vulnerable) %>%
    tbl_summary()
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```

## Treatment Self Regulation Questionnaire (TSRQ)
### Missing values of subscale scores
Missing indicates that all responses within a subscale were either not answered or the participant selected "Prefer not to answer." 
```{r}
data_lst %>%
  purrr::map(
    ~.x %>%
    select(TSRQ_auto:TSRQ_amot) %>%
    mutate(across(TSRQ_auto:TSRQ_amot, ~ factor(.x, levels  = c("Missing", "Not Missing")))) %>%
    tbl_summary()
  ) %>%
  tbl_merge(., tab_spanner = spanner)
```

### Mean subscale scores
* Missing values as shown in the previous table are not included in the 
```{r}
# Display the data
data_lst %>%
  purrr::map( 
    ~.x %>%
    select(tsrq_auto_score:tsrq_amot_score) %>%
    tbl_summary(
      statistic = list(all_continuous() ~ "{mean} ({sd})"),
      missing = "always")
  ) %>%
  tbl_merge(.,tab_spanner = spanner)
```

```{r}
#| eval: false

# checking Jun's plot of the response rates of the sms surveys
sms %>% 
  filter(redcap_event_name %in% c("week02", "week03", "week04", "week06")) %>% 
  select(hsqid, smoke1, redcap_event_name) %>%
  mutate(smoke1 = ifelse(is.na(smoke1), 0, 1)) %>%
  group_by(hsqid) %>%
  pivot_wider(names_from = redcap_event_name, values_from = smoke1) %>%
  ungroup() %>%
  left_join(
    data %>% filter(hsqid %in% sms$hsqid) %>% select(hsqid, arm) %>% distinct(),
    by  = "hsqid") %>%
  select(week02:arm) %>%
  tbl_summary(by = arm) %>%
  add_p()
```
