---
title: "HSQ - Baseline Characteristics Quantitative Measures (draft)"
date: today

format: 
  docx:
    reference-doc: "D:\\custom-reference-doc.docx"
    toc: true

execute: 
  echo: false
  warning: false
---


```{r}
#| eval: false
# -----------------------------------------------------------------------------
# Carlos Rodriguez, PhD. CU Anschutz Dept. of Family Medicine

# Date: 10/23/2025

# Description: This script is designed to tabulate the quantitative measures 
# for the HSQ baseline characteristics manuscript

# Inputs: Requires .csv files in the analyses_sas folder. The .csv files are
# created from various scripts such as the primary outcomes completion report,
# prepare_network_data.qmd, and the NJH dev_prep_data.py scripts.

# Relies on custom functions in the 
# [dfm_tb](https://github.com/carlosivanr/dfm_tb) package

# Save to the following drive
# "Z:\Shared\DFM\HSQ_Shared\Analysis\Stat Working\Baseline Paper"
# -----------------------------------------------------------------------------
```


```{r}
# Load libraries
library(tidyverse)
library(magrittr, include = "%<>%")
library(gtsummary)
library(dfmtbx)
```


# RedCap Participant Management Project Data
```{r}
# Reads a .csv file created from the primary outcomes completion report
hsq <- read_csv("C:\\Users\\rodrica2\\OneDrive - The University of Colorado Denver\\Documents\\DFM\\projects\\hsq\\analyses_sas\\data\\hsq_data.csv", show_col_types = FALSE)

# Filter to baseline only
hsq %<>%
  filter(event_name == "0mo")
```


## Demographics
```{r}
hsq %>% 
  mutate(Hispanic = eth,
         Arm = arm,
         Gender = gender,
         Age = age) %>%
  select(Arm, Age, Gender, Hispanic, Race) %>%
  tbl_summary(by = Arm,
    statistic = list(Age ~ "{mean} ({sd})"),
    digits = list(
      all_categorical() ~ c(0,1), # The first value is for the n, and the second value for the %
      all_continuous() ~ c(2,2))  # the first value is for mean, the second value is for sd
  ) %>%
  add_overall() %>%
  add_p(
    test = list(Age ~ "t.test"),
    test.args = list(Age ~ list(var.equal = TRUE)),
    pvalue_fun = label_style_pvalue(digits = 3)
  )
```

{{< pagebreak >}}

```{r}
# Sum se1 through se5 as subscale from Jim Cunningham's work https://www.sciencedirect.com/science/article/pii/S2212962614000583
```

## Scored psychological measures
- PHQ4 (psy_score)
- PHQ4 depression subscore (dep_score)
- PHQ4 anxiety subscore (anx_score)
- Abstinence Related Motivational Engagement (arme_score)
- Proactive Coping Scale (pcs_score)
- Treatment Self Regulation Questionnaire
  - Autonomous motivation (factor 1, tsrq_auto)
  - Introjected regulation (factor 2, tsrq_intr)
  - External regulation (factor 3, tsrq_extr)
  - Amotivation (factor 4, tsrq_amot)
- Self efficacy (se_confidence) *** needs confirmation on scoring
- Residual attraction to smoking (cd_attraction)
- Continuing smoker self-label (cd_smoker)
- Vulnerable to smoking relapse (cd_vulnerable)

```{r}
# Create two vectors of the continuous and binary variables from the 
# psychological instruments
cont_vars <- c("psy_score", "dep_score", "anx_score", "arme_score", 
               "pcs_score", "tsrq_auto", "tsrq_intr", "tsrq_extr", 
               "tsrq_amot", "se_confidence")

bin_vars <- c("cd_attraction", "cd_smoker", "cd_vulnerable")
```

```{r}
psy_tab <- hsq %>%
  select(arm, all_of(cont_vars), all_of(bin_vars)) %>%
  tbl_summary(
    by = arm,
    type = list(all_of(cont_vars)  ~ "continuous"),
    statistic = list(all_of(cont_vars) ~ "{mean} ({sd}), [{min}; {median}; {max}]"),
    digits = list(
      all_categorical() ~ c(0,1), # The first value is for the n, and the second value for the %
      all_continuous() ~ c(2,2)),  # the first value is for mean, the second value is for sd
    missing = "ifany",
    label = list(
      psy_score = "PHQ4 (PHQ2 + GAD2)",
      dep_score = "PHQ2 (depresion)",
      anx_score = "GAD2 (anxiety)",
      arme_score = "Abstinence Related Motivational Engagement",
      pcs_score = "Proactive Coping Scale",
      tsrq_auto = "TSRQ Autonomous Motivation",
      tsrq_extr = "TSRQ External Regulation",
      tsrq_intr = "TSRQ Introjected Regulation",
      tsrq_amot = "TSRQ Amotivation",
      cd_attraction = "CD Residual attraction",
      cd_smoker = "CD Continuing smoker self-label",
      cd_vulnerable = "CD Vulnerable to smoking relapse",
      se_confidence = "Self Efficacy (CAM RTTI)")) %>%
  add_overall() %>%
  add_p(pvalue_fun = label_style_pvalue(digits = 3))
  # add_p(
  #   test = list(all_continuous() ~ "t.test"),
  #   test.args = all_continuous() ~ list(var.equal = TRUE))
```

```{r}
psy_tab
```

{{< pagebreak >}}


## SE Questions
```{r}
se_qs <- c("se6", "se7", "se8", "se9", "se10", "se11", "se12")
```


```{r}
# Gave error on se8 for some reason
hsq %>%
  select(arm, all_of(se_qs)) %>%
  mutate(across(all_of(se_qs), ~ factor(.x, levels = c(
    "Very sure I am able to", 
    "Usually sure I am able to", 
    "Somewhat sure I am able to", 
    "Neutral",  
    "Somewhat not sure I am able to",
    "Usually not sure I am able to",
    "Not at all sure I am able to",
    "Prefer not to answer" 
    )))) %>%
  tbl_summary(
    by = arm,
    digits = all_categorical() ~ c(0,1),
    label = list(
      se6 = "Are you able to keep thinking of the pros of quitting when you feel like smoking?",
      se7 = "Are you able to coach yourself 'I want to quit' or 'I won't give up'?",
      se8 = "Are you able to keep thinking of the cons of smoking when you feel like smoking?",
      se9 = "Are you able to ask the people around you to support your quit attempt?",
      se10 = "Are you able to tell smokers you have quit smoking when you are at a party?",
      se11 = "Are you able to anticipate situations in which it might be difficult to refrain from smoking?",
      se12 = "Are you able to divert yourself when you feel like smoking?"
    )) %>%
  add_overall() %>%
  add_p(test.args = all_categorical() ~ list(workspace = 2e7),
        pvalue_fun = label_style_pvalue(digits = 3))           

```

```{r}
#| eval: false
hsq %>% 
  filter(arm == "Control") %>%
  select(tsrq_extr) %>%
  ggplot(., aes(x = tsrq_extr)) +
  geom_histogram()
```

```{r}
#| eval: false
hsq %>% 
  filter(arm != "Control") %>%
  select(tsrq_extr) %>%
  ggplot(., aes(y = tsrq_extr)) +
  geom_boxplot()
```

```{r}
#| eval: false
hsq %>% 
  select(tsrq_extr, arm) %>%
  ggplot(., aes(y = tsrq_extr, x = arm)) +
  geom_boxplot()
```

## Social Network Metrics
```{r}
pna <- read_csv(
  "C:\\Users\\rodrica2\\OneDrive - The University of Colorado Denver\\Documents\\DFM\\projects\\hsq\\analyses_sas\\data\\hsq_network_data.csv", 
  show_col_types = FALSE) %>%
  filter(event_name == "0mo")
```

```{r}
pna %>%
  select(arm, density, n_components, homophily_gender, homophily_age_cat, btw_centr, deg_centr) %>% 
  tbl_summary(
    by = arm,
    stat = list(
      density ~ "{mean} ({sd}), [{min}; {median}; {max}]",
      homophily_gender ~ "{mean} ({sd}), [{min}; {median}; {max}]",
      homophily_age_cat ~ "{mean} ({sd}), [{min}; {median}; {max}]",
      btw_centr ~ "{mean} ({sd}), [{min}; {median}; {max}]",
      deg_centr ~ "{mean} ({sd}), [{min}; {median}; {max}]",
      n_components ~ "{mean} ({sd}), [{min}; {median}; {max}]"
    ),
    label = list(
      density = "Density",
      n_components = "Number of components",
      btw_centr = "Betweenness centralization",
      deg_centr = "Degree centralization",
      homophily_gender = "homophily (gender)",
      homophily_age_cat = "homophily (age)"
    )
  ) %>%
  add_overall() %>%
  add_p(
    test = everything() ~ "wilcox.test",
    pvalue_fun = label_style_pvalue(digits = 3))
```

<!-- # NJH Data -->
<!-- !!! Variable preparation can be found in the srnd.qmd document, just copy and paste from there!!! -->
```{r}
njh <- read_csv("C:\\Users\\rodrica2\\OneDrive - The University of Colorado Denver\\Documents\\DFM\\projects\\hsq\\analyses_sas\\data\\njh_data_20260219.csv", show_col_types = FALSE)
```

```{r}
# Dependence by psychological measures

# Dependence is captured as a categorical meaures in the NJH data(SI 9)

# Pyschological variables include the ARME and the TSRQ
# The ARME is a continuous measure after its scored

# The TSRQ has 4 sub domains, that are continuous as well
```

```{r}
# Data prep to order factors for these columns that are specific to each tbco type.
how_soon_cols <- njh %>%
  select(
    "SI 9",
    "OI 9-3",
    # "OI 9-2", # References Pipe but not in data
    "OI 9-1",
    "OI 9-4",
    "OI 9-5") %>%
  names()

njh %<>%
  mutate(across(all_of(how_soon_cols), ~ factor(.x, levels = c(
    "Within five minutes",
    "6 to 30 minutes",
    "31 to 60 minutes",
    "More than 60 minutes",
    "Don't know",
    "Refused"))))
```

```{r}
# Merge hsq and njh data
hsq <- hsq %>%
  left_join(njh, by = c("hsqid" = "Hsqid"))
```

```{r}
# The SI 9 column has branching logic to only those that responded Yes to "Smoke Cigarettes"
hsq %>% 
  select(tsrq_auto:tsrq_amot, `SI 9`) %>%
  drop_na(`SI 9`) %>%
  tbl_summary(by = `SI 9`) %>%
  add_overall()
```


```{r}
hsq %>% 
  select(arme_score, `SI 9`) %>%
  drop_na(`SI 9`) %>%
  tbl_summary(,
    by = `SI 9`,
    statistic = list(everything() ~ "{mean} ({sd}), [{min}; {median}; {max}]")) %>%
  add_overall()
```


```{r}
hsq %>% 
  select(arme_score, `SI 9`, arm) %>%
  drop_na(`SI 9`) %>%
  tbl_strata(
  strata = arm,
  .tbl_fun = 
    ~ .x %>%
    tbl_summary(
      by = `SI 9`,
      statistic = list(
        everything() ~ "{mean} ({sd}), [{min}; {median}; {max}]")) %>%
    add_overall()
  )
```