---
title: "HSQ Alter Survey"
date: today
format:
  html:
    toc: true
    html-math-method: katex
    embed-resources: true

execute:
  echo: false
  warning: false
---

```{r, echo = FALSE, eval = FALSE}
################################################################################
# Carlos Rodriguez, PhD. CU Anschutz, Dept. of Fam. Medicine
# Helpers stay quit - Alter survey report

# This report is designed to count frequencies and proportions of the missing
# and non-missing values for the primary and secondary outcomes as defined in
# the statistical analysis plan.

# In addition, this report scores and summarizes the instruments used in the HSQ
# surveys. Finally, this report will export .csv files for importing into SAS.
################################################################################
```

```{r, load libraries, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(magrittr, include = "%<>%")
pacman::p_load(here,
               tidyverse,
               gtsummary,
               gt,
               install = FALSE)
```

```{r}
source(here("scripts/functions/get_redcap_data.R" ))
```

```{r}
data <- get_redcap_data(26172)

data %<>%
  filter(asking_for_your_feedback_complete == 2)
```

# Number of completed records
```{r}
data %>%
  select(asking_for_your_feedback_complete) %>%
  tbl_summary()
```

# When you talked with participant about smoking, which of the following did you discuss?
```{r}
data %<>%
  mutate(a4_cat = factor(
    recode(a4, 
           `0` = "Reason to quit (cost; health risks and benefits)",
           `1` = "Readiness to quit",
           `2` = "How they might help you quit",
           `3` = "Offered handouts or materials",
           `4` = "Medications that help quitting (like nicotine patches or prescription meds)",
           `5` = "Referral to a quitline",
           `6` = "Other"), 
    levels = c("Reason to quit (cost; health risks and benefits)",
              "Readiness to quit",
              "How they might help you quit",
              "Offered handouts or materials",
              "Medications that help quitting (like nicotine patches or prescription meds)",
              "Referral to a quitline",
              "Other")))
```


```{r}
data %>%
  select(a4_cat) %>%
  tbl_summary(label = a4_cat ~ "Topics discussed")
```


```{r}
data %>%
  filter(a4_cat == "Other") %>%
  mutate(a4_other = ifelse(is.na(a4_other), "Unknown", a4_other)) %>%
  select(a4_other) %>% 
  tbl_summary(label = a4_other ~ "Other topics")
```

# How would you describe your smoking status?	
```{r}
data %<>%
  mutate(a5_cat = factor(
    recode(a5, 
           `0` = "I quit in the last 6 months",
           `1` = "I quit in the last 30 days",
           `2` = "I am ready to quit",
           `3` = "I am thinking about quitting in the next 30 days",
           `4` = "MedicationsI am ready to quit in the next 6 months",
           `5` = "I am not ready to quit",
           `6` = "I was never a smoker"), 
    levels = c("I quit in the last 6 months",
              "I quit in the last 30 days",
              "I am ready to quit",
              "I am thinking about quitting in the next 30 days",
              "I am ready to quit in the next 6 months",
              "I am not ready to quit",
              "I was never a smoker")))
```

```{r}
data %>%
  select(a5_cat) %>%
  mutate(a5_cat = fct_na_value_to_level(a5_cat, level = "Unknown")) %>%
  tbl_summary(label = a5_cat ~ "Describe smoking status")
```

# Was this your ﬁrst conversation with participant about smoking?
```{r}
data %<>%
  mutate(a6_cat = factor(recode(a6, 
                         `0` = 'No',
                         `1` = "Yes",
                         `2` = "I don't remember"),
                         levels = c("No", "Yes", "I don't remember")))
```


```{r}
data %>%
select(a6_cat) %>%
  tbl_summary(label = a6_cat ~ "First smoking conversation")
```

# Did you do anything diﬀerently since talking to participant about smoking?
```{r}
data %<>%
  mutate(a7_cat = factor(recode(a7, 
                         `0` = 'No',
                         `1` = "Yes"),
                         levels = c("No", "Yes")))
```

```{r}
data %>%
  select(a7_cat) %>%
  tbl_summary(label = a7_cat ~ "Yes")
```

## What did you do diﬀerent?
```{r}
data %>%
  filter(a7_cat == "Yes") %>%
  select(a7_what) %>%
  mutate(a7_what = ifelse(is.na(a7_what), "Unknown", a7_what)) %>%
  tbl_summary(label = a7_what ~ "What did you do different")

```

# Has your smoking status changed?
```{r}
data %<>%
  mutate(a8_cat = factor(recode(a8, 
                         `0` = 'No',
                         `1` = "Yes, I have quit",
                         `2` = "Yes, I am thinking about quitting"),
                         levels = c("No", "Yes", "Yes, I am thinking about quitting")))
```


```{r}
data %>%
  select(a8_cat) %>%
  mutate(a8_cat = fct_na_value_to_level(a8_cat, level = "Unknown")) %>%
  tbl_summary()
```

# Was it helpful having a conversation with participant?
```{r}
data %<>%
  mutate(a9_cat = factor(recode(a9, 
                         `0` = 'Extremely',
                         `1` = "Very",
                         `2` = "Moderately",
                         `3` = "Slightly",
                         `4` = "Not at all"),
                         levels = c('Extremely', "Very", "Moderately", "Slightly","Not at all")))
```

```{r}
data %>%
  select(a9_cat) %>%
  tbl_summary(label = a9_cat ~ "Helpful")
```

# How would you feel about having another conversation with participant about smoking in the future?
```{r}
data %>%
  select(a10) %>%
  tbl_summary(label = a10 ~ "Feelings about future conversations")
```

# Is there anything else you want to say about your conversation with participant?
```{r}
data %>%
  select(a11) %>%
  tbl_summary(label = a11 ~ "Additional comments")
```

